### 2010-07-25 papers/icfp-2010-desc/paper_idesc.tex
Desc@ICFP: cut on the conclusive US instructor speech. Add a \newspace so that Discussion is on its own page.

Hence completing our implementation of the open terms interpreter.
We have defined a well-typed language of arithmetical expressions,
taking advantage of indexing. Then, we have implemented an evaluator
for closed term, based on the generic catamorphism function. Using the
free monad construction, we have automatically derived the language of
open terms. Using its monadic structure, we have implemented the
interpreter for open terms in context. Without much effort, we
have described the syntax of a well-typed language, together with its
semantics.

@@

>>>>

Hence completing our implementation of the open terms
interpreter. Without much effort, we have described the syntax of a
well-typed language, together with its semantics.

@@

\newpage
